---
title: "Final Exam R Notebook"
author: "Jacob Joy"
output: html_notebook
---

```{r}
library(dplyr)
library(ggplot2)
library(caret)
library(corrplot)
library(factoextra)



#Laptop Data import
fuelDF = read.csv("C:\\EIA923.csv")
```
```{r}
set.seed(7165)
str(fuelDF)

fuelDF_CH = fuelDF %>% select(-plant_id_eia, -plant_id_eia_label)

fuelDF_CH.num = fuelDF_CH %>% select(-fuel_type_code_pudl)

fuelDF_CH.norm = scale(fuelDF_CH.num)

summary(fuelDF_CH)

#gasDF = fuelDF %>% filter(fuel_type_code_pudl == 'gas') 

colMeans(is.na(fuelDF_CH))

fuelDF_CH$fuel_type_code_pudl = as.factor(fuelDF_CH$fuel_type_code_pudl)

boxplot(fuelDF_CH$fuel_received_units)

dummy_fuel = dummyVars(~fuel_type_code_pudl, data = fuelDF_CH)
dummy_matrix = predict(dummy_fuel, fuelDF_CH)
fuelDF_CH.dummy = cbind(dummy_matrix, fuelDF_CH)
fuelDF.clean = cbind(fuelDF_CH.num, fuelDF_CH.dummy)

cor_matrix = data.frame(cor(fuelDF_CH.norm))

```
# K-Means Clustering
```{r}
clusters = kmeans(fuelDF.clean, centers = 3)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
